\LARGE \bf Planning with Attitude

### 2020-10-10 paper/main.tex
More updates to flexible sat.

    \begin{algorithm} 
    	\begin{algorithmic}[1]
    		\caption{Multiplicative Gauss-Newton Method}\label{alg:mgn}
    		\State $k = 0$
    		\While{significant progress}
    		    \State $\bar{J} = \pdv{r(q_k)}{q} G(q_k)$ \Comment{quaternion adjusted Jacobian}
    		    \State $ \phi = -(\bar{J}^T \bar{J})^{-1} \bar{J}^T r(q_k)$ 
    		    \State $q_{k+1} = q_k \otimes \varphi(\phi)$ \Comment{apply step multiplicatively}
    		    \State $k = k + 1$
    		\EndWhile
    	\end{algorithmic}
    \end{algorithm}

@@

    \subsection{Satellite Attitude Keep-Out}
    A spacecraft with flexible appendages modes must perform a 150 degree slew, while making sure that a startracker does not look within 40 degrees of the sun. The flexible body spacecraft dynamics are based on the truncated hybrid coordinate model, with the three largest modes captured \cite{Tracy2020}. We can guarantee the startracker body fixed vector ($^Br_{st}$) does not look within 40 degrees of the inertial sun vector ($^Nr_{sun}$) by formulating the following constraint:
    \begin{equation}
        \langle ^N A ^B {}^Br_{st} , ^Nr_{sun}\rangle \leq \cos(40 ^\circ).
    \end{equation}
    From this constraint, an eigen-axis slew trajectory planner may violate this constraint \cite{markley2014fundamentals}. ALTRO is able to reason about the nonlinear flexible spacecraft dynamics, actuator constraints, and the startracker line of sight constraint.
        \begin{figure}
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a dedicated keep out zone. Attitude is parameterized with a Rodrigues parameter to visualize in 3D. The constraint surface represents attitudes where the startracker is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able reason about the keep out zone.}
        \end{figure}

>>>>

    \begin{algorithm} 
    	\begin{algorithmic}[1]
    		\caption{Multiplicative Gauss-Newton Method}\label{alg:mgn}
    		\State $k = 0$
    		\While{significant progress}
    		    \State $\bar{J} = \pdv{r(q_k)}{q} G(q_k)$ \Comment{quaternion adjusted Jacobian}
    		    \State $ \phi = -(\bar{J}^T \bar{J})^{-1} \bar{J}^T r(q_k)$ 
    		    \State $q_{k+1} = L(q_k) \varphi(\phi)$ \Comment{apply step multiplicatively}
    		    \State $k = k + 1$
    		\EndWhile
    	\end{algorithmic}
    \end{algorithm}

@@

    \subsection{Satellite Attitude Keep-Out}
    A spacecraft with flexible appendages modes must perform a 150 degree slew, while ensuring that a star tracker does not look within 40 degrees of the sun. The attitudes that result in the star tracker looking too close to the sun will be referred to as a keep-out zone. The flexible body spacecraft dynamics are based on the truncated hybrid coordinate model, with the three largest modes captured \cite{Tracy2020}. We can guarantee the star tracker body fixed vector ($^Br_{st}$) does not look within 40 degrees of the inertial sun vector ($^Nr_{sun}$) by formulating the following constraint:
    \begin{equation}
        \langle ^N A ^B {}^Br_{st} , ^Nr_{sun}\rangle \leq \cos(40 ^\circ).
    \end{equation}
    Due to this constraint on the feasible attitudes, an eigen-axis slew trajectory planner may end up violating this keep out zone \cite{markley2014fundamentals}. ALTRO can generate a feasible trajectory for this problem since it is able to reason about the nonlinear flexible spacecraft dynamics, actuator constraints, and the star tracker line of sight constraint.
        \begin{figure}
            \centering
            \includegraphics{figures/kevins_plots/attitude_slew_plot.tikz}
            \caption{Visualization of the flexible spacecraft slew with a dedicated keep out zone. Attitude is parameterized with a Rodrigues parameter to visualize in three dimensions. The constraint surface represents attitudes where the star tracker is within 40$^\circ$ of the sun. The unconstrained solution violates this constraint, while the constrained solution is able reason about the keep out zone.}
        \end{figure}
